\chapter{Introduction} %!chapter
% books overall approach
NOTE: I don't know if this should be the introduction or conclusion.

As the title of the book suggests, what comes after this is almost a reflection of what makes mathematics, it would be too arrogant to wish to provide this reflection as it has turned out to be broad without borders everything now is in some form of mathematics.
\section{How to get most of this book????????}
\section{What is Mathematics?}
"Mathematics is the study of quantity"\footnote[1]{https://www.newyorker.com/culture/culture-desk/what-is-mathematics}. Telling you that this is a more accurate meaning would be lying but as far as we go with your pursuit of mathematics you will discover the messy and not so attractive meaning of this field of study. Mathematicians as you will become are always fascinated with quantity how much is how much. If we say James\footnote[1]{This name will frequently be used, you can feel free to substitute(replace) with your name} is 12 years old what do we mean? How much big is ten people than two? These questions and far far more advanced than this is what inspired people to develop mathematics to create rules which we will discover on dealing with quantities, manipulating quantities, thinking about quantities and what ever is possible with quantity. Perhaps you will in future invent or discover some of these rules as you become a better mathematics student.

\section{The Reality of Mathematics}
This is one of the most debated topic in mathematics. Are numbers or what we know about mathematics real and that we found them already existing waiting to be found and that we found them or we invented them, we created them from our own imagination like the way we create all the stuff found on earth books, bicycles. As you are starting this book, I can not convincingly tell you the answer or you can find this question a little bit silly but as we go on with our discussion on mathematics you will realize how important this question is or how unreal some math concepts are and you wonder whether everything else is real or not?. Hannah Fry spends a lot of considerable amount of time discussing the reality of mathematics in \href{https://www.youtube.com/watch?v=cyvDG8qjt-M&list=PLVk3tArtG-kju2RYzpvh99RiL8hHA9ORV}{magic of numbers}
\section{Why Mathematics}
%importance of mathematics in life
\section{Branches of Mathematics}

\section{Bonus: }%!BONUS
\section{Lookup: }%!LOOKUP
\section{Glossary}
\section{References}

\newpage