\chapter{Things and Objects}%!chapter

\section{what are things and objects}
The world is filled with things and objects those we see and those we don't see. There are animals that are vastly available in the world of different types [examples]. Every other animal is taken to be distinct a sheep is different from another sheep. Therefore a sheep is a thing and another sheep is another thing, They are of the same type of course they belong to a group of animals called sheep. A cow is different from another cow . Therefore a cow is a thing and another cow is another thing, They are of the same type, they belong to a group of animals of cattle. This can be said of [this] thing and [another] thing. Addition property can be that "this" in [this] thing can be a sheep and "another" in [another] thing can be a cow and also this relationship of [this] and [another] is also those things are distinct. But, what if we have a [this] and another [this] belonging to one group lets say group of cattle and we have [another] thing and another [another] thing, how can we be sure that those distinct things equal to one another and how can we express it not so laboriously as we have done because we can have as many [this(es)] and [another(s)] as we want and using word [this] and [another] has shown not a good way to go about it. And Mathematics provide a way to compare a group of [this] and  and a group of [that]. mathematics provide us with numbers as a sneak way to talk about [this] and [another], a clever way to talk about quantity. This makes mathematics just another form of language in this case, a language that gives all the languages superpower to express ambiguous ideas or situations. In our case the situation was on distinctiveness how to say how much of distinct is a group from another group without comparing [this].

%one way of comparing is lining things head to head -- distinct to distinct to check if the groups are of equal or not  -- how can we express the difference of one group from another?%
\section{Glossary}
\section{References}
